### 2021-03-02 background.tex
Background

The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security. The sandboxing technique comprises of two steps. First, rules are miner and will compose the sandbox,
%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
through test generator tools. These tools explore program behavior and monitor access to sensitive APIs. The second stage ensures that resources not accessed, or accessed differently, at first stage, are denied access. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

>>>>

The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security. The sandboxing technique comprises of two steps. First, rules are mined and will compose the sandbox,
%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
through test generator tools \kn{This sentence seems to miss something "what" happens through test generation tools.} . These tools explore program behavior and monitor access to sensitive APIs. The second stage ensures that resources not accessed, or accessed differently than first stage, are denied access. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.
